Analysis 2 - Models

### 2025-04-11 analysis/2_choco.qmd
sample2

---
title: "Analysis 2 - Models"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
execute: 
  cache: false
---

@@

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(ggdist)
library(brms)
```

@@

```{r}
df <- read.csv("https://raw.githubusercontent.com/RealityBending/FakeFace/refs/heads/main/data/data.csv") |> 
  mutate(Real = (Belief_Answer + 1) / 2,  # Rescale
         Orientation = ifelse(Sexual_Orientation == "Straight ", "Heterosexual", Sexual_Orientation),
         Item = gsub(".jpg", "", Stimulus)) |> 
  filter(Sex %in% c("Male", "Female"), Orientation %in% c("Heterosexual", "Bisexual", "Homosexual")) |> 
  mutate(Relevance = case_when(
    Sex == "Male" & Orientation == "Heterosexual" & grepl("NF", Stimulus) ~ "Relevant",
    Sex == "Female" & Orientation == "Heterosexual" & grepl("NM", Stimulus) ~ "Relevant",
    Sex == "Male" & Orientation == "Bisexual" & grepl("NF", Stimulus) ~ "Relevant",
    Sex == "Female" & Orientation == "Bisexual" & grepl("NM", Stimulus) ~ "Relevant",
    Sex == "Male" & Orientation == "Homosexual" & grepl("NM", Stimulus) ~ "Relevant",
    Sex == "Female" & Orientation == "Homosexual" & grepl("NF", Stimulus) ~ "Relevant",
    .default = "Irrelevant"
  )) |> 
  filter(Relevance == "Relevant") |> 
  select(Participant, Sex, Item, Real, Attractive, Beauty)

@@

write.csv(df, "../data/sample1.csv", row.names = FALSE)
```

@@

make_ppcheck  <- function(m, fill = "#FF9800") {
  pred <- m |> 
    insight::get_predicted(data = df[sample(nrow(df), 1000, replace = FALSE), ], 
                           predict="prediction", iterations = 100) |>
    bayestestR::reshape_iterations()

  pred |>
    ggplot(aes(x = iter_value)) +
    stat_bin(aes(group = iter_group, y = after_stat(count / max(count))), position = "identity",
             geom="bar", breaks = seq(-0.005, 1.005, by = 0.01), pad = TRUE,
             alpha = 0.01, fill = fill) + 
    stat_bin(data = df, aes(x = Real, y = after_stat(count / max(count))), 
             geom="step", breaks = seq(-0.01, 1.0, by = 0.01),  pad = TRUE, 
             linewidth = 1, color = "#9C27B0") + 
    scale_y_sqrt() +
    scale_x_continuous(expand = c(0, 0)) +
    theme_minimal() 
}

@@

```{r}
g1_zoib <- modelbased::estimate_grouplevel(m1_zoib)
plot(g1_zoib)

@@

# modelbased::estimate_grouplevel(insight::download_model("brms_chocomini_1"))
# modelbased::estimate_grouplevel(insight::download_model("brms_chocomini_1"), type = "total")
# performance::performance_dvour(g1)
```

@@

@@

```{r}
df <- read.csv("https://raw.githubusercontent.com/RealityBending/FakeFace2/refs/heads/main/data/data_task.csv")
df$Real <- (df$Realness + 1) / 2  
df <- df[c("Participant", "Item", "Real", "Attractive", "Beauty")]
```

>>>>

---
title: "Analysis 2 - Models"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
execute: 
  cache: true
---

@@

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(ggdist)
library(brms)
library(cmdtsanr)
```

@@

```{r}
#| eval: false

df <- read.csv("https://raw.githubusercontent.com/RealityBending/FakeFace/refs/heads/main/data/data.csv") |> 
  mutate(Real = (Belief_Answer + 1) / 2,  # Rescale
         Orientation = ifelse(Sexual_Orientation == "Straight ", "Heterosexual", Sexual_Orientation),
         Item = gsub(".jpg", "", Stimulus)) |> 
  filter(Sex %in% c("Male", "Female"), Orientation %in% c("Heterosexual", "Bisexual", "Homosexual")) |> 
  mutate(Relevance = case_when(
    Sex == "Male" & Orientation == "Heterosexual" & grepl("NF", Stimulus) ~ "Relevant",
    Sex == "Female" & Orientation == "Heterosexual" & grepl("NM", Stimulus) ~ "Relevant",
    Sex == "Male" & Orientation == "Bisexual" & grepl("NF", Stimulus) ~ "Relevant",
    Sex == "Female" & Orientation == "Bisexual" & grepl("NM", Stimulus) ~ "Relevant",
    Sex == "Male" & Orientation == "Homosexual" & grepl("NM", Stimulus) ~ "Relevant",
    Sex == "Female" & Orientation == "Homosexual" & grepl("NF", Stimulus) ~ "Relevant",
    .default = "Irrelevant"
  )) |> 
  filter(Relevance == "Relevant") |> 
  select(Participant, Sex, Item, Real, Attractive, Beauty)

@@

write.csv(df, "../data/sample1.csv", row.names = FALSE)
```
```{r}
df <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionChoco/refs/heads/main/data/sample1.csv")
df$Sex <- factor(df$Sex, levels = c("Male", "Female"))
```

@@

make_ppcheck  <- function(m, fill = "#FF9800") {
  pred <- m |> 
    modelbased::estimate_prediction(df[sample(nrow(df), 4000, replace = FALSE), ], keep_iterations = 200) |>
    select(Sex, starts_with("iter_")) |> 
    # insight::get_predicted(data = df[sample(nrow(df), 1000, replace = FALSE), ],
    #                        predict="prediction", iterations = 5) |>
    # as.data.frame() |> 
    bayestestR::reshape_iterations()

  pred |>
    ggplot(aes(x = iter_value)) +
    stat_bin(aes(group = iter_group, y = after_stat(count / max(count))), position = "identity",
             geom="bar", breaks = seq(-0.005, 1.005, by = 0.01), pad = TRUE,
             alpha = 0.01, fill = fill) + 
    stat_bin(data = df, aes(x = Real, y = after_stat(count / max(count))), 
             geom="step", breaks = seq(-0.01, 1.0, by = 0.01),  pad = TRUE, 
             linewidth = 1, color = "#9C27B0") + 
    scale_y_sqrt() +
    scale_x_continuous(expand = c(0, 0)) +
    theme_minimal() +
    facet_wrap(~Sex, scales = "free_y")
}

@@

```{r}
g1_zoib <- modelbased::estimate_grouplevel(m1_zoib)
plot(g1_zoib)
performance::performance_dvour(g1_zoib)

@@

# modelbased::estimate_grouplevel(insight::download_model("brms_chocomini_1"))
# modelbased::estimate_grouplevel(insight::download_model("brms_chocomini_1"), type = "total")

@@

```{r}
#| eval: false

df <- read.csv("https://raw.githubusercontent.com/RealityBending/FakeFace2/refs/heads/main/data/data_task.csv") |> 
  filter(Relevance == "Relevant") |> 
  mutate(Real = (Realness + 3) / 6,
         Attractive = Attractiveness / 6,
         Beauty = Beauty / 6) |> 
  select(Participant, Sex=Gender, Condition, Item=Stimulus, Real, Attractive, Beauty)

write.csv(df, "../data/sample2.csv", row.names = FALSE)
```
```{r}
df <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionChoco/refs/heads/main/data/sample2.csv")
df$Sex <- factor(df$Sex, levels = c("Male", "Female"))
```

@@
